Mental Well-Being

### 2023-02-17 docsrc/documentation/notebooks/mental_well_being.Rmd
updating sphinx to have root level file paths. tidying. matching new development changes to transition models

---
title: "Mental Well-Being"
output: html_document
bibliography: 
  - "refs.bib" # switch bibliography position. depending on where the file is being run. stick to this one when compiiling the website using the makefile
  #- "../../refs.bib" # use this one if knitting directly in Rstudio. Easier for debugging.
---

@@

```{r setup, include=FALSE}
source('sphinx_notebook_utils.R')
```

@@

```{r neighbourhood_barchart, echo=FALSE}
continuous_density("SF_12")
```
### Data

@@

```{r housing_output, echo=FALSE}
options(width=120)
ols_histogram("../../../data/transitions/test/sf12_ols_2018_2019.rds", "y")
ols_output("../../../data/transitions/test/sf12_ols_2018_2019.rds")
```

>>>>

---
title: "Mental Well-Being"
output: html_document
bibliography: 
  - "docsrc/refs.bib"
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir= "../minos")
```

@@

```{r load_data, include=FALSE}
source("docsrc/documentation/notebooks/sphinx_notebook_utils.R")
```

@@

```{r SF12_Density}
continuous_density("data/transitions/SF_12/OLS/SF_12_2018_2019.rds", "next_SF_12")  
```

### Data

@@

```{r SF12_Output, echo=FALSE}
options(width=120)
ols_output("data/transitions/SF_12/OLS/SF_12_2018_2019.rds")
ols_histogram("data/transitions/SF_12/OLS/SF_12_2018_2019.rds", "next_SF_12")
```
